High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-10-08 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

\title[V4046\,Sgr high-resolution ALMA observations]{V4046\,Sgr high-resolution 1.3\,mm continuum ALMA observations: a disc with a thin ring}

@@

Disc structures can be explored by means of comparing mm continuum and scattered-light images. These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane. By comparing both, is easier to determine whether asymmetries in scattered-light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.

>>>>

\title[High-resolution ALMA observations of V4046\,Sgr]{High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring}

@@

Disc structures can be explored by means of comparing mm continuum and scattered-light images. These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane. By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
